### 2017-03-21 main.tex
Final edits, merges, PDFs (main and diff).

We found these parameters to work well across a variety of target
syllables, but various other parameter sets yield results similar to
those presented here.  Some of the parameters trade off detection
accuracy or temporal precision vs.~training time. For example,
decreasing the frame interval generally decreases both latency and
jitter, but also increases training time. Sometimes the effects are
syllable-specific: for example, using a 30-ms time window rather than
50 ms speeds training while usually having a minimal effect on
detector performance, but occasionally a syllable will be seen for
which extending the window to 80 ms is very helpful.

>>>>

We found these parameters to work well across a variety of target
syllables, but various other parameter sets yield results similar to
those presented here.  Some of the parameters trade off detection
accuracy or temporal precision vs.~training time. For example,
decreasing the frame interval generally decreases both latency and
jitter, but also increases training time. Sometimes the effects are
syllable-specific: for example, using a 30-ms time window rather than
50 ms speeds training while usually having a minimal effect on
detector performance (as is the case, for example, for all of the
detection points for lny64), but occasionally a syllable will be seen
for which extending the window to 80 ms is helpful.
